Performance Comparison of Common Face Detection APIs using Video Stills from Professional Tennis Matches

### 2018-02-06 paper/paper.Rmd
trying to get rid of pandoc errors

toc: false
fig_caption: yes
number_sections: false
fontsize: 11pt
header-includes:
    - \usepackage{booktabs}
    - \usepackage{longtable}
bibliography: references.bib
biblio-style: chicago
output: rticles::asa_article
link-citations: true
---

@@

- The faces were recorded if it showed their face at a minimum of 20 by 20 pixels. 
- The back of the head was not detected as a face by any software, these areas were classified manually but reclassified as other.
- Crowd faces were not the intended targets of the recognition however these faces contributed to our understanding of the software. 
- The same face size standard applied to crowd members, but focus was placed on the most prominent faces.

@@

grid.arrange(plots1, plots2, nrow=2)

@@

- Animetrics: Animetrics Face Recognition API, FaceR API by @Animetrics.

- Google: Google Cloud Vision API [-@Google]

- Microsoft: Microsoft Azure Cognitive Services Face API, published by @Microsoft.

- Skybiometry: @Skybiometry the spin off detection and recognition software of Neurotechnology.

@@

- ManualClassifiedFaces.csv contains the data collected on each face by manual tagging.
- ManualClassifiedScenes.csv contains scene information about each image.

>>>>

toc: false
fig_caption: yes
number_sections: false
fontsize: 11pt
bibliography: references.bib
biblio-style: chicago
output: rticles::asa_article
link-citations: true
---

@@

\begin{itemize}
\item The faces were recorded if it showed their face at a minimum of 20 by 20 pixels. 
\item The back of the head was not detected as a face by any software, these areas were classified manually but reclassified as other.
\item Crowd faces were not the intended targets of the recognition however these faces contributed to our understanding of the software. 
\item The same face size standard applied to crowd members, but focus was placed on the most prominent faces. 
\end{itemize}

@@

grid.arrange(plots1, plots2, nrow=2)
```

@@

\begin{itemize}
\item Animetrics: Animetrics Face Recognition API, FaceR API by @Animetrics.
\item Google: Google Cloud Vision API [-@Google]
\item Microsoft: Microsoft Azure Cognitive Services Face API, published by @Microsoft.
\item Skybiometry: @Skybiometry the spin off detection and recognition software of Neurotechnology. 
\end{itemize}

@@

\begin{itemize}
\item ManualClassifiedFaces.csv contains the data collected on each face by manual tagging.
\item ManualClassifiedScenes.csv contains scene information about each image.
\end{itemize}
